### 2013-03-28 menger.tex
Added example of markov menger game

  \begin{definition}
    In the two-player game $\mengame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $S$ choosing a finite subcollection $\mathcal{F}_n\subseteq\mathcal{U}_n$. $S$ wins if $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{definition}

  \begin{theorem}
    $X$ is Menger if and only if $S \win \mengame{X}$.
  \end{theorem}

@@

    Since $X$ is Lindelof, we can assume $C$ plays only countable covers of $X$. Then, since $S$ is choosing finite subsets, we may assume $S$ chooses some initial segement of the countable cover. In turn, we can assume $C$ plays an increasing open cover $\{U_0,U_1,\dots\}$ where $U_n\subseteq U_{n+1}$. And in that case, it's suffient to assume $S$ simply chooses a singleton subset of each cover. And finally, since choices made by $S$ are already covered, we can assume that every open set in a cover played by $C$ covers the sets chosen by $S$ previously.

@@

    We may observe that if $S$ can find an $f:\omega\to\omega$ such that $\bigcup_{n<\omega}U_{f\rest (n+1)} = X$, she can use $\{U_{f\rest 0}\}, \{U_{f\rest 1}\}, \dots$ to counter $C$'s strategy.

@@

>>>>

  \begin{definition}
    In the two-player game $\mengame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $F$ choosing a finite subcollection $\mathcal{F}_n\subseteq\mathcal{U}_n$. $F$ wins if $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{definition}

  \begin{theorem}
    $X$ is Menger if and only if $C \not\win \mengame{X}$.
  \end{theorem}

@@

    Since $X$ is Lindelof, we can assume $C$ plays only countable covers of $X$. Then, since $F$ is choosing finite subsets, we may assume $F$ chooses some initial segement of the countable cover. In turn, we can assume $C$ plays an increasing open cover $\{U_0,U_1,\dots\}$ where $U_n\subseteq U_{n+1}$. And in that case, it's suffient to assume $F$ simply chooses a singleton subset of each cover. And finally, since choices made by $F$ are already covered, we can assume that every open set in a cover played by $C$ covers the sets chosen by $F$ previously.

@@

    We may observe that if $F$ can find an $f:\omega\to\omega$ such that $\bigcup_{n<\omega}U_{f\rest (n+1)} = X$, she can use $\{U_{f\rest 0}\}, \{U_{f\rest 1}\}, \dots$ to counter $C$'s strategy.

@@

  \begin{proposition}
    $X$ is compact if and only if $F \tactwin \mengame{X}$
  \end{proposition}

  \begin{proof}
    Assume $X$ is compact. For each open cover played by $C$, pick the finite subcover.

    Assume $F$ has a winning tactical strategy. For any open cover, have $C$ play only it during the entire game. $F$'s only choice must be a finite subcover.
  \end{proof}

  \begin{proposition}
    If $X$ is $\sigma$-compact then $F \markwin \mengame{X}$
  \end{proposition}

  \begin{proof}
    Let $X=\bigcup_{n<\omega} X_n$ for compact $X_n$. On round $n$, $F$ picks the finite subcover of $C$'s open cover of $X_n$.
  \end{proof}

  Due to Telgarski in ``On Games of Topsoe'':

  \begin{theorem}
    For metrizable $X$, $X$ is $\sigma$-compact if and only if $F \win \mengame{X}$.
  \end{theorem}

  In a question I posed to G, he answered:

  \begin{lemma}
    For all $\alpha_0, \alpha_1, \dots < \omega_1$ and functions $\tau:\omega_1\times\omega \rightarrow [\omega_1]^{<\omega}$, $\{\tau(\alpha_n,n): n<\omega\}$ is not a cover for $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$.
  \end{lemma}

  \begin{proof}
    Let $P_n = \{\beta: \beta < \alpha \Rightarrow \beta \in \tau(\alpha, n)\}$. Observe that each $P_n$ is finite; else there is some $\alpha$ larger than every member of $P_n$ such that $P_n \subseteq \tau(\alpha, n)$.

    Choose $\beta \not\in \bigcup_{n<\omega} P_n$. Then for each $n<\omega$, pick $\alpha_n>\beta$ such that $\beta \not\in \tau(\alpha_n, n)$.
  \end{proof}

  Note that the one-point Lindel\"ofication of discrete $\omega_1$, $\oneptlind{\omega_1}$, is not $\sigma$-compact. With the above lemma, we may see that:

  \begin{example}
    $F \win \mengame{\oneptlind{\omega_1}}$ but $F \not\markwin \mengame{\oneptlind{\omega_1}}$.
  \end{example}

  \begin{proof}
    First, we see $F$ has a simple perfect information strategy: in response to the initial cover of $\oneptlind{\omega_1}$, $F$ chooses a co-countable neighborhood of $\infty$. On successive turns she may pick a single set from $C$'s covers to cover the countable remainder.

    Now, suppose that $\sigma(\mc{U}, n)$ was a winning Markov strategy and aim for a contradiction. Consider the covers \[\mc{U}(\alpha) = \{[\alpha,\omega_1)\cup\{\infty\}\} \cup \{\{\beta\}:\beta < \alpha\}\] and define $\tau(\alpha,n)$ to be the union of singletons chosen by $\sigma(\mathcal{U}(\alpha),n)$. As $\sigma$ was a winning strategy, for all $\alpha_0, \alpha_1, \dots < \omega_1$, $\{\sigma(\mathcal{U}(\alpha_n),n): n<\omega\}$ must cover $\oneptlind{\omega_1}$, and thus $\{\tau(\alpha_n,n): n<\omega\}$ must cover $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$, contradiction.
  \end{proof}

  The question remains:

  \begin{question}
    Does $F \markwin \mengame{X}$ imply $X$ is $\sigma$-compact?
  \end{question}

  % Let $\sigma(\mathcal{U},n)$ be $F$'s winning Markov strategy.
